### 2022-05-21 main/chapter_2ljets.tex
add draft rjr summary figure

>>>>

\begin{figure}[tp]
\centering
\begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/2ljets_rjr_23l_2l_summary.png}
    \caption{$2\ell$}
\end{subfigure}
\hfill
\begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/2ljets_rjr_23l_3l_summary.png}
    \caption{$3\ell$}
\end{subfigure}
\\[0.5em]
\begin{subfigure}{0.99\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/2ljets_rjr_summary_log.pdf}
    \caption{$\twoljets$}
\end{subfigure}
\caption{%
\TODO{summary plots with the previous 2/3l excesses and $\twoljets$.}
\TODO{reproduced from / made by the RJR team}
}
\label{fig:2ljets_signal_examples}
\end{figure}
